---
title: "SMC_NAC_dataAnnotate"
author: "Lala M Motlhabi"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 8
    keep_md: no
    output:
      pandoc_args:
      - +RTS
      - -K64m
      - -RTS
    self_contained: no
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( cache=TRUE )
knitr::opts_chunk$set( echo=TRUE )
knitr::opts_chunk$set( message=FALSE )
knitr::opts_chunk$set(warning=FALSE )
knitr::opts_chunk$set(autodep=TRUE)
options(figcap.prefix = "Figure", figcap.sep = ":", figcap.prefix.highlight = "**")
options(tabcap.prefix = "Table", tabcap.sep = ":", tabcap.prefix.highlight = "**")
```
```{r config}
install.packages("ssh.utils")
library(ssh.utils)
library(dplyr)
library(DT)
library(reshape2)
library(mongolite)
library(stringr)
library(tidyverse)
library(tidyr)
library(data.table)
library(getopt)
library(reshape2)
library(magrittr)

library(stringr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(data.table)
library(getopt)

```




##########
#
# Examples on how to update the config files using R
#
##########



### Load & backUp the original config files
```{r backUpcurrentCofigs}
print("Opening current config files")
clinical_types  <-fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_clinical_types.txt', header=TRUE);
omics_types  <-fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_omics_types.txt', header=TRUE);
unique_var  <-fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_unique_variables.txt', header=TRUE);21539836
samples <- fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_samples.txt', header=TRUE)

### Copy original files to the deprecated folder just for backup

# copy the files to the new folder :/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/

print("Creating backup of current config files")
file.copy('/LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_clinical_types.txt', '/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_clinical_types.txt', overwrite = TRUE) 
file.copy('/LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_omics_types.txt', '/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_omics_types.txt', overwrite = TRUE)
file.copy('/LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_unique_variables.txt', '/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_unique_variables.txt', overwrite = TRUE)
file.copy('/LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_samples.txt', '/LJ/CompBio/share/data/omics/VIP/portal_data/data/deprecated_08122018/vip_samples.txt', overwrite = TRUE)
```

##Omics_types

```{r Omicsupdate}

  print("Processing omics data file")
  new_omics_data = readRDS("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/ConfigFiles/new_omics_type.RDS");
  #print(head(new_omics_data))
  # print("Updating omics types")
  #Add values to omics_types.txt from a file that contains the data to load in the database
  # This file contains the list of unique variables that are available for selection from the omics_data collection in mongo
  new_omics_types = new_omics_data %>% dplyr::select(TYPE, DATA_TYPE, CATEGORY, VALUE_TYPE) %>% 
    dplyr::distinct(TYPE, DATA_TYPE, CATEGORY, VALUE_TYPE)
 
  # Join the new unique variables to the existing ones and do a distinct to make sure that there are no duplicates.
  omics_types = dplyr::bind_rows(omics_types,new_omics_types) %>% dplyr::distinct() %>% dplyr::arrange(TYPE)
```

 ##unique omics variables 
```{r getuniqueOmicsVars}
  print("Updating unique omics variables")
  #Add values to the unique_variables file from a file that contains the data to load in the database.
  # This file is used to populate the variable selection menus on the left side of the browser
  # We need to merge the PROJECT NAME and CANCER TYPE into a single column as it is how the tree library in R is providing the data.
  # Also do a distinct to remove duplicates.

 new_unique_omics_variables<-readRDS("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/ConfigFiles/new_unique_omics_variables.RDS")

#new_omics_data$PROJECT_SELECTION = paste0(PROJECT_NAME,".",CANCER_TYPE,new_omics_data$PROJECT_SELECTION)
 new_unique_omics_variables<- new_unique_omics_variables %>% dplyr::transmute(PROJECT_SELECTION = PROJECT_SELECTION,
                                                                   TYPE = TYPE,
                                                                   DATA_TYPE,
                                                                   VARIABLE,
                                                                   CATEGORY) %>%
    dplyr::distinct(PROJECT_SELECTION, TYPE, DATA_TYPE, VARIABLE, CATEGORY)
 
  # Join the new variables with the existing ones and remove duplicates in case the variable already exist in the config file
  unique_var = dplyr::bind_rows(unique_var,new_unique_omics_variables) %>% dplyr::distinct() %>% dplyr::arrange(PROJECT_SELECTION, CATEGORY, TYPE, VARIABLE)
```

##Get Unique Samples
```{r getUniqueSamples}

  print("Updating unique samples")
new_samples<-readRDS("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/ConfigFiles/new_samples.RDS")
  # Make new samples (if any) available from the config file
  new_samples  %>% dplyr::select(PROJECT_NAME, SAMPLE_NAME, SAMPLE_TYPE, CANCER_TYPE) %>% 
    dplyr::distinct(PROJECT_NAME, SAMPLE_NAME, SAMPLE_TYPE, CANCER_TYPE)
  new_samples %<>% mutate_if(is.factor,as.character)
  # Join with previous existing samples and distinct to make sure there are no duplicates.
  
    
  samples = dplyr::bind_rows(samples, new_samples) %>% dplyr::distinct() %>% dplyr::arrange(PROJECT_NAME, CANCER_TYPE, SAMPLE_NAME, SAMPLE_TYPE)
  
```
#clinical_data
```{r clinicalData}

  print("Processing clinical data file")
  new_clinical_data = readRDS("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/ConfigFiles/new_clinical_types.RDS")
  
  print("Updating clinical data types")
  #Add values to omics_types.txt from a file that contains the data to load in the database
  new_clinical_types = new_clinical_data  %>% dplyr::distinct(TYPE, DATA_TYPE, CATEGORY, VALUE_TYPE)
 #ifelse("VALUE_TYPE" %in% colnames(new_omics_data), VALUE_TYPE,)
                                                                              
  clinical_types = dplyr::bind_rows(clinical_types,new_clinical_types) %>% dplyr::distinct() %>% dplyr::arrange(TYPE)
  
  print("UPdating unique clinical variables")
  #Add values to the unique_variables file from a file that contains the data to load in the database
  new_unique_clinical_variables = readRDS("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/ConfigFiles/new_unique_clinical_variables.RDS")
  new_unique_clinical_variables=new_unique_clinical_variables  %>% dplyr::distinct(PROJECT_SELECTION, TYPE, DATA_TYPE, VARIABLE, CATEGORY)
  
  unique_var = dplyr::bind_rows(unique_var,new_unique_clinical_variables) %>% dplyr::distinct() %>% dplyr::arrange(PROJECT_SELECTION, CATEGORY, TYPE, VARIABLE)
```

#Update Current configs
```{r}
print("Saving updated config files")
samples %<>% mutate_if(is.factor,as.character)
clinical_types %<>% mutate_if(is.factor,as.character)
omics_types %<>% mutate_if(is.factor,as.character)
unique_var %<>% mutate_if(is.factor,as.character)
write.table(clinical_types, file= "/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_clinical_types.txt", quote = FALSE, sep = "\t", row.names = FALSE)
write.table(omics_types, file= "/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_omics_types.txt", quote = FALSE, sep = "\t", row.names = FALSE)
write.table(unique_var, file= "/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_unique_variables.txt", quote = FALSE, sep = "\t", row.names = FALSE)
write.table(samples, file= '/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_samples.txt', quote = FALSE, sep = "\t", row.names = FALSE)

```

#Copy Config files to server
vip_dev server location : /opt/shiny-server/samples/sample-apps/vip-dev/data/vip_omics_types.txt
backup_location :/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/final_uploadData/configFiles/current_configFiles_backUP

previously loactions with the most current staged and updated config files:
/LJ/CompBio/share/data/omics/VIP/portal_data/data/

```{bash copyConfigFilesToserver}
 #first get the old files from the server to back them up
 #ssh into shiny app_server
 farm103
 
 #cp over omics_type
cp /LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_omics_types.txt /opt/shiny-server/samples/sample-apps/vip-dev/data/vip_omics_types.txt

 #cp over updated clinical_type #new_size 15019 
 cp /LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_clinical_types.txt /opt/shiny-server/samples/sample-apps/vip-dev/data/vip_clinical_types.txt

#cp over unique_vars 
cp  /LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_unique_variables.txt /opt/shiny-server/samples/sample-apps/vip-dev/data/vip_unique_variables.txt

#cp over samples_types
cp /LJ/CompBio/share/data/omics/VIP/portal_data/data/vip_samples.txt /opt/shiny-server/samples/sample-apps/vip-dev/data/vip_samples.txt



```

#Add Date_Uploaded Field
```{r}
vipfiles<-list.files("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData",pattern=".RDS$", full.names=T)

for(i in seq_along(vipfiles)){
  anno<-readRDS(vipfiles[i])
  anno$DATE_UPLOADED<-Sys.Date()
  saveRDS(anno,file=vipfiles[i])
  viptab<-sub("RDS$","tab",vipfiles[i])
  write.table(anno,file=viptab,sep="\t",row.names=F,na="",quote=F)
  rm(anno)
}



```
1.started @4:30PM took less than an hour 
2.started @8:36pm
```{bash}
mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cibersort_fraction.tab
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cibersort.tab         
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cin.tab               
 mongoimport --port 27018 --db VIP --collection clinical_data_dev  --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_clinical_info.tab     
mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cn_amplified.tab      
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cn_deleted.tab        
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cnv.tab               
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_cytscore.tab          
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_estimate_info.tab     
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_expression.tab        
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_gsva.tab              
 mongoimport --port 27018 --db VIP --collection clinical_data_dev  --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_mutation_burden.tab   
mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_mutation_signature.tab
 mongoimport --port 27018 --db VIP --collection omics_data_dev --type tsv --ignoreBlanks --headerline --file /LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData/vip_smc_mutations.tab         
     
```

#Validate Upload
```{r mongolite, eval=F}

m<-mongolite::mongo("omics_data_dev", db="VIP",url="mongodb://lj-compbio-dev103:27018")
m$count() #1686067698

#see how data looks like
m$iterate()$one()

#How many distinct "PROJECT_NAME"
length(m$distinct("PROJECT_NAME"))

#SMC
m$count('{"PROJECT_NAME" : "SMC_NAC" }') #11332069
test<-m$find('{"PROJECT_NAME" : "SMC_NAC","TYPE":"ESTIMATE"}')#,"CATEGORY":"Summary statistic"}')
m$update('{"PROJECT_NAME" : "SMC_NAC","TYPE":"ESITIMATE","CATEGORY":"Summary statistic"}', '{"$set":{"CATEGORY":"Summary statistics"}}')
```

#3T studio
```{bash}
 db.getCollection("omics_data_dev").find({"PROJECT_NAME":"SMC_NAC","TYPE":"CYTOLYTIC ACTIVITY"})
db.omics_data_fix.update(
   { "PROJECT_NAME":"SMC_NAC","TYPE":"CIN SCORE" },
   { $set: { "CATEGORY": "Summary statistics" } }
)

db.omics_data_fix.updateMany(
   { "PROJECT_NAME":"SMC_NAC","TYPE":"CYTOLYTIC ACTIVITY" },
   { $set: { "CATEGORY": "Summary statistics" } }
)

db.omics_data_dev.updateMany(
   { "PROJECT_NAME":"SMC_NAC","TYPE":"ESTIMATE" },
   { $set: { "CATEGORY": "Summary statistics" } }
)

db.omics_data_dev.updateMany(
   { "PROJECT_NAME":"SMC_NAC","TYPE":"CIN SCORE" },
   { $set: { "CATEGORY": "Summary statistics" } }
   
   
###Remove- Delete COPY NUMBER
db.getCollection("omics_data_dev").find({"PROJECT_NAME":"SMC_NAC","TYPE":"COPY NUMBER"})


db.omics_data_dev.deleteMany( { "PROJECT_NAME":"SMC_NAC","TYPE":"COPY NUMBER" } );
   
   
```


##Edit "Summary statistic" in config files

```{r}
clinical_types  <-fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_clinical_types.txt', header=TRUE);
omics_types  <-fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_omics_types.txt', header=TRUE);
unique_var  <-fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_unique_variables.txt', header=TRUE);
samples <- fread('/LJ/CompBio/share/data/omics/VIP/portal_data/data/tmp_config_staging/vip_samples.txt', header=TRUE)


head(clinical_types)

omics_types$CATEGORY<-gsub("Summary statistic$","Summary statistics",omics_types$CATEGORY)
unique(unique_var$CATEGORY)
unique_var$CATEGORY<-gsub("Summary statistic$","Summary statistics",unique_var$CATEGORY)

```


#Update reccommended changes by George
##Summary statistcs As sub-Catergory of Sa

```{r fixSummaryStats}
vipfiles<-list.files("/LJ/CompBio/share/data/omics/SMC_neoadj/vip_data_upload/SMC_neoadj_2018_6_21/vip_curatedData",pattern=".RDS$", full.names=T)
sumstats<-vipfiles[c(5,9:10,4)]

clin<-readRDS(sumstats[1])
#  PROJECT_NAME  SAMPLE_NAME SAMPLE_TYPE CANCER_TYPE CLINICAL_TYPE CLINICAL_VAR DATA_TYPE  VALUE IS_COMMON           CATEGORY DATE_UPLOADED
#1      SMC_NAC OB_15_0053_1       Tumor      BREAST      Clinical       Gender  discrete FEMALE         Y Sample annotations    2018-08-14
#2      SMC_NAC OB_15_0058_1       Tumor      BREAST      Clinical       Gender  discrete FEMALE         Y Sample annotations    2018-08-14
#3      SMC_NAC OB_15_0058_3       Tumor      BREAST      Clinical       Gender  discrete FEMALE         Y Sample annotations    2018-08-14
#4      SMC_NAC OB_15_0066_3       Tumor      BREAST      Clinical       Gender  discrete FEMALE         Y Sample annotations    2018-08-14
#5      SMC_NAC OB_15_0067_1       Tumor      BREAST      Clinical       Gender  discrete FEMALE         Y Sample annotations    2018-08-14

tab<-readRDS(sumstats[2])

names(tab)
```

:%s/summary statistics/Summary statistics/g

db.omics_data_dev.updateMany(
   { "PROJECT_NAME":"SMC_NAC","TYPE":"ESTIMATE" },
   { $set: { "CATEGORY": "Sample annotations","TYPE": "Sample annotations" } }
   

